Dark Control: The Default Mode Network as a Reinforcement Learning Agent

### 2018-08-07 paper/paper.tex
Update Fg 1 & 4 + correct BibTex compilation error

\begin{figure}[!h]
  \includegraphics[width=.9\linewidth]{neurobiological_overview_DMN.pdf}
  \caption{\textbf{Default mode network: key functions.}
  Neurobiological overview of the DMN with its major constituent parts and
  the associated functional roles relevant in our functional interpretation.
  The blue horizontal line indicates the cytoarchitectonic border between the
  more dorsal BA9 and the more ventral BA10 (Brodmann, 1909).
  %
  Axonal tracing in monkeys and diffusion tractography in humans suggested
  that the NAc of the reward circuitry has monosynaptic fiber connections
  to the vmPFC \citep{haber1995, croxson2005quantitative}. Evaluation of
  propagated value information and triggered affective states encoded
  in the vmPFC may then feed into the functionally connected partner nodes of
  the DMN, such as the dmPFC and PMC \citep{andrews2010, bzdok2013segregation}.
  }
  \label{fig:neurobiological_overview_DMN}
\end{figure}
%
\subsection{The posteromedial cortex: global monitoring and information integration}
The midline structures of the human DMN,
including the posteromedial cortex (PMC) and
the medial prefrontal cortex (mPFC),
are probably responsible for highest turn-overs
of energy consumption \citep{raichle2001pnas, raichle_baseline}.
These metabolic characteristics go hand-in-hand with
brain-imaging findings that suggested the PMC and mPFC to
potentially represent the functional core of the DMN
\citep{andrews2010, hagmann2008mapping}.

@@

\subsection{The hippocampus: memory, space, and experience replay}
The DMN midline has close functional links
with the HC \citep{henceforth implying to include also parahippocampal regions}
in the medial temporal lobe \citep{vincet2006, shannon2013morning} \textemdash
a region long known to be involved in
memory operations and spatial navigation in animals and humans.
While the HC
is traditionally believed to allow recalling past experience,
there is now increasing evidence for an important role
in constructing mental models in general
\citep{maguire2016, schacter2007remembering, gelbard2008internally, Javadi2017,
boyer2008evolutionary}.
Its recursive anatomical architecture
may be specifically designed to allow reconstructing
entire sequences of experience from memory fragments.
Indeed,
hippocampal damage was
not only associated with an impairment in re-experiencing the past (i.e., amnesia),
but also forecasting of one's own future and
imagination of experiences more broadly \citep{hassabis2007patients}.

@@

Additionally,
the DMN was proposed to be situated
at the top of the brain network hierarchy, with
the subordinate salience and dorsal attention network in the middle and
the primary sensory cortices at the bottom
\citep{carhart2010default, margulies2016situating}.
Its putative involvement in thinking about 
hypothetical experiences and future outcomes
appears to tie in with the implicit computation of
action and state cascades as a function of
experienced events and collected feedback from the past.
A policy matrix encapsulates the choice probabilities of possible actions
on the world given a current situation (i.e., state).
The DMN may subserve
  constant exploration of candidate action trajectories and
  nested estimaton of their
  cumulative reward outcomes. Implicit computation of future choices
  provides a potential explanation for the
  evolutionary emergence and practical usefulness of
  mind-wandering at day-time and dreams during sleep
  in humans.
\begin{figure}[!h]
  \includegraphics[width=.9\linewidth]{neurobiological_and_rl_overview_DMN.pdf}
  \caption{\textbf{Default mode network:
  possible neurobiological implementation of reinforcement learning.}
  Overview of how the constituent regions of the DMN (refer to section \ref{sec:nodes}) may
  map onto computational components necessary for an RL agent.
  %
  Axonal tracing in monkeys and diffusion tractography in humans suggested
  that the NAc of the reward circuitry has monosynaptic fiber connections
  to the vmPFC \citep{haber1995, croxson2005quantitative}. Evaluation of
  propagated value information and triggered affective states encoded
  in the vmPFC may then feed into the functionally connected partner nodes of
  the DMN, such as the dmPFC and PMC \citep{andrews2010, bzdok2013segregation}.
}
  \label{fig:rl_process_chart}
\end{figure}

>>>>

\begin{figure}[!h]
  \includegraphics[width=.9\linewidth]{neurobiological_overview_DMN.pdf}
  \caption{\textbf{Default mode network: key functions.}
  Neurobiological overview of the DMN with its major constituent parts and
  the associated functional roles relevant in our functional interpretation.
  The blue horizontal dashed line indicates the cytoarchitectonic border between the
  more dorsal BA9 and the more ventral BA10 \citep{brodmann1909vergleichende}.
  %
  Axonal tracing in monkeys and diffusion tractography in humans suggested
  that the NAc of the reward circuitry has monosynaptic fiber connections
  to the vmPFC \citep{haber1995, croxson2005quantitative}. Evaluation of
  propagated value information and triggered affective states encoded
  in the vmPFC may then feed into the functionally connected partner nodes of
  the DMN, such as the dmPFC and PMC \citep{andrews2010, bzdok2013segregation}.
  }
  \label{fig:neurobiological_overview_DMN}
\end{figure}
%
\subsection{The posteromedial cortex: global monitoring and information integration}
The midline structures of the human DMN,
including the posteromedial cortex (PMC) and
the medial prefrontal cortex (mPFC),
are probably responsible for highest turn-overs
of energy consumption \citep{raichle2001pnas, raichle_baseline}.
These metabolic characteristics go hand-in-hand with
brain-imaging findings that suggested the PMC and mPFC to
potentially represent the functional core of the DMN
\citep{andrews2010, hagmann2008mapping}.

@@

\subsection{The hippocampus: memory, space, and experience replay}
The DMN midline has close functional links
with the HC (henceforth implying to include also parahippocampal regions)
in the medial temporal lobe \citep{vincet2006, shannon2013morning} \textemdash
a region long known to be involved in
memory operations and spatial navigation in animals and humans.
While the HC
is traditionally believed to allow recalling past experience,
there is now increasing evidence for an important role
in constructing mental models in general
\citep{maguire2016, schacter2007remembering, gelbard2008internally, Javadi2017,
boyer2008evolutionary}.
Its recursive anatomical architecture
may be specifically designed to allow reconstructing
entire sequences of experience from memory fragments.
Indeed,
hippocampal damage was
not only associated with an impairment in re-experiencing the past (i.e., amnesia),
but also forecasting of one's own future and
imagination of experiences more broadly \citep{hassabis2007patients}.

@@

Additionally,
the DMN was proposed to be situated
at the top of the brain network hierarchy, with
the subordinate salience and dorsal attention network in the middle and
the primary sensory cortices at the bottom
\citep{carhart2010default, margulies2016situating}.
Its putative involvement in thinking about 
hypothetical experiences and future outcomes
appears to tie in with the implicit computation of
action and state cascades as a function of
experienced events and collected feedback from the past.
A policy matrix encapsulates the choice probabilities of possible actions
on the world given a current situation (i.e., state).
The DMN may subserve
  constant exploration of candidate action trajectories and
  nested estimaton of their
  cumulative reward outcomes. Implicit computation of future choices
  provides a potential explanation for the
  evolutionary emergence and practical usefulness of
  mind-wandering at day-time and dreams during sleep
  in humans.
\begin{figure}[!h]
  \includegraphics[width=.9\linewidth]{neurobiological_and_rl_overview_DMN.pdf}
  \caption{\textbf{Default mode network:
  possible neurobiological implementation of reinforcement learning.}
  Overview of how the constituent regions of the DMN (refer to section \ref{sec:nodes}; blue horizontal dashed line indicates the border between BA9 and BA10) may
  map onto computational components necessary for an RL agent.
  %
  Axonal tracing in monkeys and diffusion tractography in humans suggested
  that the NAc of the reward circuitry has monosynaptic fiber connections
  to the vmPFC \citep{haber1995, croxson2005quantitative}. Evaluation of
  propagated value information and triggered affective states encoded
  in the vmPFC may then feed into the functionally connected partner nodes of
  the DMN, such as the dmPFC and PMC \citep{andrews2010, bzdok2013segregation}.
}
  \label{fig:rl_process_chart}
\end{figure}
